---
title: "Data Carpentry Report"
author: "DRB"
date: "June 2, 2016"
output: html_document
---
##Global settings 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=11)
```

##Load the data and libraries
First, we load the _portal_ data from http://kbroman.org/datacarp/ then we installed _dplyr_ and _ggplot2_libraries.

The initial data set has `r nrow(surveys)' rows and 'r ncol(surveys)' columns.


Then we down load and install the analysis packages
install.packages("dplyr")
install.packages("ggpolot2")

```{r, load_data}
## download.file(url, filename)
url <- "http://kbroman.org/datacarp/portal_data_joined.csv"
filename <- "portal_data_joined.csv"
surveys <- read.csv ("portal_data_joined.csv")

```

Then we load them...

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
```

##Clean the data a bit 
Enter codes used to filter for data and clean up noise...
```{r}
surveys_complete <- surveys %>% filter(!is.na(hindfoot_length))%>% filter (!is.na(weight)) %>% filter (sex != "")
```

## Some boring histogram
Enter codes used to create the graphs
```{r}
surveys_complete %>% ggplot (aes(x=weight)) +
  geom_histogram(bins=100) 
```

## Some colorful scatter plots
```{r}
surveys_complete %>% 
filter(species_id %in% c("DM", "DS", "DO")) %>%
ggplot (aes(x=weight, y=hindfoot_length)) +
geom_point(aes(color=species_id, shape=species_id))    
```

## Some tables of data

This makes a simple table (looks better ifyou have more columns)...
knitr::kable(tab)

This library performs the same function but has more options
library(xtable)
xtable

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
